---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
title: "Estimation de la température du couvert et comparaison de méthodes d’estimation de la conductance stomatique sur le site ICOS FR-Bil."
author:
  - name: '**Tom Taborski**'
    affil: 1
    main: true
    orcid: '0000-0002-1099-3857'
    email: tom.taborski@inrae.fr
  - name: "Christophe Chipeaux"
    affil: 1
    main: false
    email: 'ag.con@posterdown.net'
  - name: "Jean-Christophe Domec"
    affil: 1
    main: false
  - name: "Denis Loustau"
    affil: 1
    main: false
affiliation:
  - num: 1
    address: ISPA, Bordeaux Sciences Agro, INRAE, F-33140, Villenave d’Ornon, France
main_findings:
  - "La mesure de la température foliaire en utilisant une es caméra thermique est non intrusif et précis."
  - "Ceci permet d'améliorer notre compréhension de la réponse des écosystèmes à leur environnement."
logoleft_name: poster_INSU_files/logos.png
logoright_name: poster_INSU_files/QR_INSU_poster.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true

primary_colour: "#275662"
secondary_colour: "#275662"
title_textsize: "80px"
main_textsize: "100px"
main_textalign: "left"
font_family: "Raleway"
main_fontfamily: "Raleway Bold"
main_height: "30in"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction

La température foliaire ($T_f$) est un paramètre impactant fortement les processus physiques et biochimiques de cet organe. Pour autant sa mesure sans biai à toujours été un défi pour les biologistes. Le développement de caméras thermiques à fortes résolution permet aujourd'hui sans perturber l'environnement des feuilles (aiguilles dans notre cas) de mesure la température de surface de ces organes.

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. Déployer et valider un dispositif de mesure de la température foliaire sur le long terme
3. utiliser une équation de flux pour estimer la conductance stomatique
4. Comparer cette estimation à d'autres méthodse plus classiques. 

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

# Results

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# References
